---
title: "slickR Basics"
author: "Jonathan Sidi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{slickR Basics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r}
library(htmlwidgets)
library(slickR)
```

## Simple carousel
Let's start easy: show the team logos one at a time

```{r}
slickR(obj = nba_team_logo$uri, height = 100, width = "95%", slideId = 'ex1')
```

Let's remove the dots with the slickOpts argument

```{r}

slickR(obj = nba_team_logo$uri, 
       slideId = 'ex2', 
       slickOpts = list(dots = FALSE), 
       height = 100, 
       width = "95%")

```


There are many more settings you can define, such as `autoplay`. For all the settings go to [slick.js](http://kenwheeler.github.io/slick) homepage

```{r}

slickR(
  obj = nba_team_logo$uri,
  slideId = 'ex3',
  slickOpts = list(dots = TRUE,autoplay = TRUE),
  height = 100, 
  width = "95%"
)

```

## Grouped Images

There are players on each team, so lets group the starting five together and have each dot correspond with a team:

```{r}

opts <- list(initialSlide = 0, 
     slidesToShow = 5, 
     slidesToScroll = 5,
     focusOnSelect = TRUE, 
     dots = TRUE)

slickR(nba_player_logo$uri,
       slideId = 'ex4',
       slickOpts = opts,
       height = 100, 
       width = "95%")

```

## Adding Links

You can add links to each element in the slide using the `objLinks` parameter.

```{r}
slickR(nba_player_logo$uri,
       slideId = 'ex5',
       objLinks = list(nba_player_logo$player_home), 
       slickOpts = opts,
       height = 100, 
       width = "95%")
```


## Replacing the dots

Sometimes the dots won't be informative enough so we can switch them with an HTML object, such as text or other images. We can pass to the `customPaging` argument javascript code using the `htmlwidgets::JS` function. 

### Replace dots with text

```{r}

cP1 <- htmlwidgets::JS("function(slick,index) {
                            return '<a>'+(index+1)+'</a>';
                       }")

opts <- list(
    initialSlide = 0,
    slidesToShow = 5,
    slidesToScroll = 5,
    focusOnSelect = TRUE,
    dots = TRUE,
    customPaging = cP1
    )

slickR(
  obj = nba_player_logo$uri,
  dotObj = nba_team_logo$uri,
  slideId = 'ex6',
  slickOpts = opts,
  height = 100,
  width = "95%"
) 

```

### Replace dots with Images

```{r}

cP2 <- JS("function(slick,index) {
          return '<a><img src= ' + dotObj[index] + '  width=100% height=100%></a>';
          }")

opts <- 
  list(
    initialSlide = 0,
    slidesToShow = 5,
    slidesToScroll = 5,
    focusOnSelect = TRUE,
    dots = TRUE,
    customPaging = cP2
  )

slick <- slickR(
  obj = nba_player_logo$uri,
  dotObj = nba_team_logo$uri,
  slideId = 'ex7',
  slickOpts = opts,
  height = 100,
  width = "95%"
) 


# Putting it all together in one slickR call
s2 <- htmltools::tags$script(
  sprintf("var dotObj = %s", jsonlite::toJSON(nba_team_logo$uri))
)

htmltools::browsable(htmltools::tagList(s2, slick))
```

## Synching Carousels

There are instances when you have many outputs at once and do not want to go through all, so you can combine two carousels one for viewing and one for searching.

```{r}
opts <- list(
  # 'up' options
    list(slidesToShow = 1, slidesToScroll = 1),
  # 'down' options
    list(dots = FALSE, 
         slidesToScroll = 1, 
         slidesToShow = 5,
         centerMode = TRUE, 
         focusOnSelect = TRUE)
)

synch_map <- expand.grid(list('up','down'),stringsAsFactors = FALSE)

slickR(rep(nba_player_logo$uri,2),
       slideIdx = replicate(2,seq_along(nba_player_logo$uri),simplify = FALSE),
       slideId =  c('up','down'),
       synchSlides = synch_map,
       slideType = rep('img',2),
       slickOpts = opts,
       height = 100, 
       width = "90%")
```

<br>
<br>
<br>
<br>
<br>
<br>

## Adding a Caption to Image

You can add a caption to an image by synching two carousels, where the upper is the content (e.g. image) and the bottom is the caption (p)

```{r}

slickR(
  obj         = c(nba_player_logo$uri[1:2],
                  glue::glue('<p>{nba_player_logo$name[1:2]}</p>')),
  slideType   = c('img','p'),
  slideId     = c('img','cap'),
  slideIdx    = list(c(1,2),c(3,4)),
  synchSlides = expand.grid(list('img','cap'),stringsAsFactors = FALSE),
  height      = 100,
  slickOpts   = list(list(dots=FALSE),list(dots=TRUE,arrows=FALSE))
)
```
