---
title: "slickR with Shiny"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{shiny}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r}
library(slickR)
library(svglite)
library(shiny)
```

# slickR in Shiny

The Following example is a Shiny App that creates `plot_num` histograms from `rnorm` with `n_obs` observations. These plots are placed in a slick carousel.

The use can choose between the different slick layouts

  - One single slick
  - Two slicks stacked
  - Two slicks stacked and synched

## UI

```{r}

ui <- fluidPage(
  sidebarLayout(
    sidebarPanel(

      sliderInput(inputId = "plot_num", 
                  label = "Number of Plots:", 
                  min = 1, max = 20, value = 5),
            
      sliderInput(inputId = "n_obs", 
                  label = "Number of observations:", 
                  min = 10, max = 500, value = 100),
      
      shiny::radioButtons('slick_type',
                          label = 'Carousel Type',
                          choices = c('single','stack','synch'),
                          selected = 'single',
                          inline = TRUE),
      
      shiny::verbatimTextOutput('current')
    ),
    mainPanel(
      
      slickROutput("slick_output",width='100%',height='200px')
      
      )
  )
)

```

## Server

```{r}
server <- function(input, output) {

```

### Create content for the carousel

```{r}

plots <- eventReactive(c(input$n_obs,input$plot_num),{
  
replicate(input$plot_num,{

     xmlSVG({hist(rnorm(input$n_obs),
                  col = 'darkgray',
                  border = 'white')},
            standalone=TRUE)

     },simplify = FALSE)
})

```


### renderSlickR

We create the slickR objects here

```{r}
  output$slick_output <- renderSlickR({
    
    x <- slickR(plots(),
                slideId = 'myslick',
                height = 600,
                width = '50%') + 
      settings(slidesToShow=3,centerMode=TRUE)
    
    switch(input$slick_type,
           'single' = x,
           'stack'  = x %stack% x,
           'synch'  = x %synch% x
           )

  })
```

### Observe the active slick

The htmlwidget is observed by shiny and information can be retrieved. 

Using the output name you set for the `renderSlick` object in this example it is `output$slick_output`

Using this you can interact server-side "on click" of the active carousel by accessing elements in `input$slick_output_current$`

|  Element |  Description|
|:--:|:--|
| `.clicked_slide`   | The index of the clicked element|
| `.relative_clicked`| The relative position of the clicked element|
| `.center_slide`    | The index of the center element|
| `.total_slide`     | The total number of elements in the carousel|
| `.active_slide`    | The ID of the active carousel|

```{r}

# We will store this information in a new reactive environment
active_slick <- shiny::reactiveValues()
  
shiny::observeEvent(input$slick_output_current,{
  
  clicked_slide    <- input$slick_output_current$.clicked
  relative_clicked <- input$slick_output_current$.relative_clicked
  center_slide     <- input$slick_output_current$.center
  total_slide      <- input$slick_output_current$.total
  active_slide     <- input$slick_output_current$.slide
  
  if(!is.null(clicked_slide)){
    active_slick$clicked_slide    <- clicked_slide
    active_slick$center_slide     <- center_slide
    active_slick$relative_clicked <- relative_clicked
    active_slick$total_slide      <- total_slide
    active_slick$active_slide     <- active_slide
  }
})

```

### Show in the UI the values in active_slick
 
```{r}

output$current <- renderText({
  l <- shiny::reactiveValuesToList(active_slick)
  paste(gsub('_',' ',names(l)), unlist(l),sep=' = ',collapse='\n')
})

```

```{r}
}
```

## Run the App

```{r}
shinyApp(ui = ui, server = server)

```